---
title: "Homework 6"
author: "Elise Mantell"
date: 2019-11-25
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(broom)
library(tidyr)
library(readxl)
library(ggplot2)
library(mgcv)
library(dplyr)
library(purrr)
library(modelr)
```

### Problem 1

```{r read and tidy data, message=FALSE}
bw_data = read_csv("./data/birthweight.csv") %>%
janitor::clean_names() %>%
mutate(babysex = as.factor(babysex)) %>%
mutate(frace = as.factor(frace)) %>% 
mutate(mrace = as.factor(mrace)) %>% 
mutate(malform = as.factor(malform)) 
```

##### To build this model, I will start with a few variables that we know generally have an effect on birthweight, including mother’s pre-pregnancy BMI, maternal smoking, and the sex of the baby. I deliberately chose variables that we could have information on prior to birth.

```{r fitting the model}
mine = lm(bwt ~ ppbmi + smoken + babysex, data = bw_data)
```

```{r }
mine %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(digits = 3)
```

```{r plot}
bw_data %>% 
  modelr::add_residuals(mine) %>% 
  modelr::add_predictions(mine) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() + labs(title =   "Model Residuals vs. Predicted Values")
```

##### Comparing to other models:
* One using length at birth and gestational age as predictors (main effects only)
* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r other models}
mod_2 = lm(bwt ~ blength + gaweeks, data = bw_data)
mod_3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + blength*babysex*bhead, data = bw_data)
```

```{r cv}
cv_df =
  crossv_mc(bw_data, 100) 

cv_df = 
  cv_df %>% 
  mutate(mine = map(train, ~lm(bwt ~ ppbmi + smoken + babysex, data =.x)),
         mod_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         mod_3  = map(train, ~lm(bwt ~ bhead + blength + babysex +
                              bhead*blength + bhead*babysex + 
                              blength*babysex + blength*babysex*bhead,
                              data = .x))) %>% 
  mutate(rmse_mine = map2_dbl(mine, test, ~rmse(model = .x, data = .y)),
         rmse_2 = map2_dbl(mod_2, test, ~rmse(model = .x, data = .y)),
         rmse_3 = map2_dbl(mod_3, test, ~rmse(model = .x, data = .y)))
```

```{r cv plot}
cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

##### The best model appears to be model 3 (head circumference, length, sex, and all interactions), and the worst is mine (only including variables available prior to birth).

### Problem 2
```{r read and tidy data p2, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r, bootstrapping and log betas plot, warning = FALSE, message = FALSE}
set.seed(17)
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
select(term, estimate) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>% 
  janitor::clean_names() %>%
  unnest() %>% 
mutate(log_betas = log10(intercept*tmin)) %>% 
    ggplot(aes(x = log_betas)) + geom_density() + labs(x = "Log(Beta0*Beta1)", y = "Density")
```

##### The distribution is skewed slightly to the left, but appears relatively normal.



```{r, 95ci betas, warning = FALSE, message = FALSE}
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
select(term, estimate) %>% 
  pivot_wider(
names_from = term, values_from = estimate) %>% 
  unnest() %>% 
  janitor::clean_names() %>% 
mutate(log_betas = log10(intercept*tmin)) %>% 
summarize(
lower_CI = quantile(log_betas, c(.025)),
upper_CI = quantile(log_betas, c(.975))) %>% 
  knitr::kable(digits = 4)
```

```{r, bootstrapping and rsquared plot, warning = FALSE, message = FALSE}
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  select(r.squared) %>% 
  ggplot(aes(x = r.squared)) + geom_density() + labs(x = "R-Squared", y = "Density")
```

##### Again, the distribution is skewed slightly to the left, but appears relatively normal. 

```{r, 95CI for rsquared, warning = FALSE, message = FALSE}
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(models = map(strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  select(r.squared) %>% 
summarize(
lower_CI = quantile(r.squared, c(.025)),
upper_CI = quantile(r.squared, c(.975))) %>% 
  knitr::kable(digits = 4)
```